\chapter{Boost C++ library}\label{app:boost}
Boost provides a repository for free peer-reviewed portable C++ source libraries. Boost provides a lot of quality components for developers to use and in the future some of them might become a part of the STL\footnote{Standard Template Library} library. The reason for choosing Boost was made because of the quality Boost can deliver, and this library is well documented. Furthermore Boost provides all the components needed for implementation of this project. Components used in development of this project are listed below:

\begin{description}
\item[Circular buffer]
is provided by Boost to give the developer the freedom to instantiate circular buffers of a given type. This type of buffer is also known as a ring buffer or cyclic buffer. It is essentially a data structure which forms a ring. 

\item[Thread]
is provided by Boost which enables a developer to manage multiple threads. A thread holds a task which is executed on a computer. The use of multi threading enables a developer to execute multiple tasks at the same time. This is of cause if the hardware and operating system is compatible with this behaviour, otherwise the multi threading is executed as multitasking, which is controlled by a time-division multiplexing process.

\item[CRC]
is provided by Boost to enable a developer with an easy-to-use CRC component. CRC is an abbreviation for cyclic redundancy code. The use of CRC in this project is based on the desire to check if data have been correctly sent and received.
\end{description}

The functionality used from Boost causes the team to focus on the actual assignment instead of focusing on implementing buffers, thread functionality, and CRC schemes. These implementation would take too much time as implementing these functionalities would require planing, implementation and optimisation. Boost deliver these functionalities for free, and Boost components are well documented, well tested, and yields the stability to make this project a reality.