\chapter{Group members}\label{app:members}
This appendix will serve as an introduction to each of the project group members. It briefly explains which parts of the project, each member has concerned himself with mostly and what role he has been filling. These roles originate from the Belbin team role model. As the project began, the group sat down and discussed which roles they would like to try and fill. They were selected out of a wish to learn what a particular role would involve, and not necessarily what each member is best at.

\begin{description}
\item[Alexander] Has primarily been working on the general architecture of the project, and the development of the backbone class + associated buffers.
\item[Frederik] Was primary responsible for testing. Working with the development of a uniform test-program for debugging and performance testing.
\item[Kent]
has been working with the physical layer which is the lowermost layer of the OSI-model. It has been demanding for his skills in terms of understanding the basics of, networking and data communication, digital signal processing, software development, and C++ programming. As a team player Kent still needs to work on his abilities on handling conflicts with greater dexterity.
\item[Kim] is a slem bandit
\item[Leon] is a slem bandit
\item[Rudi] has been the coordinator of this project. This has been a big challenge as he is used to focus on a single problem in depth and not on the big picture which is essential as a project coordinator. The work has primary been on the application programming interface and the associated message buffers.
\end{description}